\documentclass{sig-alternate-10pt}

\usepackage[hyphens]{url}
\usepackage{color}
\usepackage{etoolbox}
\usepackage{hyperref}
\usepackage{subcaption}

\def\Snospace~{\S{}}
\renewcommand*\sectionautorefname{\Snospace}
\renewcommand*\subsectionautorefname{\Snospace}
\renewcommand*\subsubsectionautorefname{\Snospace}
\renewcommand*{\figureautorefname}{Fig.}

\begin{document}

\input{macros}

% \conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
% \CopyrightYear{2007}
% \crdata{0-12345-67-8/90/01}
% --- End of Author Metadata ---

\title{Adaptive Stream Processing in Wide-Area Network}

\numberofauthors{1}
\author{ \alignauthor \textit{Anonymous for submission} }

\maketitle

\begin{abstract}
  In this paper, we present \sysname{}, a stream processing system that adapts
  the application execution to wide-area network changes. \sysname{} enables
  graceful degradation during resource fluctuations: trading application
  accuracy for the freshness of analytics. To achieve this, \sysname{} explores
  the PAR (performance-accuracy-resource) principle. We employ an offline
  profiling process that explores the parameter space of each application and
  generates a profile of the application. During runtime, the system would alter
  the application execution if the resource level changes. We evaluate
  \sysname{} against three real-world applications: large-scale IoT
  applications, video analytics and distributed CDN monitoring. At places where
  traditional approaches would lead to either significant application accuracy
  drop or long tail, our system gracefully handles the application.
\end{abstract}

% \category{H.4}{Information Systems Applications}{Miscellaneous}
% \terms{Theory}
% \keywords{ACM proceedings, \LaTeX, text tagging}

\input{intro}
\input{motivation}
\input{system-overview}
\input{design}
\input{implementation}
\input{evaluation}

{\bibliographystyle{acm}\bibliography{sigcomm2017}}

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
